---
title: "calculate t-statistic and p-value from group means, SDs, and sample size"
author: "David Kaiser"
date: "2018/02/23"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("t_test_means_SDs.R")
```

### Description

A function to calculate the **t-statistic** and the **p-value** from the means, standard deviations, and sample size of two groups.
The sample size can be equal or not equal but two values need to be supplied.
The t-statistic, the variance of the two groups and the degrees of freedom are calculated as described in [wikipedia](https://en.wikipedia.org/wiki/Student%27s_t-test#Independent_two-sample_t-test).
The p-value is calculated as described in a [post by Kelly Black](http://www.cyclismo.org/tutorial/R/pValues.html#calculating-a-single-p-value-from-a-t-distribution).

### Arguments

* *mean1* -- mean value of group 1
* *mean2* -- mean value of group 2
* *sd1* -- standard deviation of group 1
* *sd2* -- standard deviation of group 2
* *n1* -- sample size of group 1
* *n2* -- sample size of group 2
* *equal.variance* -- logical; are group variances assumed to be equal? defaults to FALSE

### Value

A named list in which

* "diff" = difference between the means
* "var" = variance of the two groups
* "t" = t-statistic
* "df" = degrees of freedom
* "p" = p-value

### Example

```{r example}
a <- rnorm(100)
b <- rnorm(200)
t.test.mean.sd(mean(a), mean(b), sd(a), sd(b), length(a), length(b))
mean(a) - mean(b)
t.test(a, b)
```


